Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
linear regressions

```{r regressions total sample}
install.packages("plm")
library(plm)
#example code:
#model_levels <- lm(recreation_visits ~ svr_median + svr_p10 + month_code*unit_code, data = regression_data)
#grun.fe <- plm(inv~value+capital, data = Grunfeld, model = "within")

model_simple <- plm(assist ~ floods + droughts, data = reg_data, model = "within")
summary(model_simple)
model_all <- plm(assist ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_all)
model_register <- plm(register ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data, model = "within")
summary(model_register)
```

>>>>

```{r regressions total sample}

#example code:
#model_levels <- lm(recreation_visits ~ svr_median + svr_p10 + month_code*unit_code, data = regression_data)

model_simple <- lm(assist ~ floods + droughts, data = reg_data)
summary(model_simple)
model_all <- lm(assist ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data)
summary(model_all)
model_register <- lm(register ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data)
summary(model_register)
